---
title: "BioCmirrors: Health Status Checks"
author:
  - name: Marcel Ramos
    affiliation: CUNY School of Public Health, New York, NY
date: "`r BiocStyle::doc_date()`"
vignette: |
  %\VignetteIndexEntry{BioCmirrors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    toc_float: true
package: BioCmirrors
---

# BioCmirrors

## Introduction 

The `BioCmirrors` package provides functions to check the health status of
Bioconductor mirrors. The package is useful for users who want to ensure that
the mirror they are using is up-to-date and has all the packages available. The
package also provides a list of all available mirrors and their statistics.
The capital `C` in `BioCmirrors` is intentional to be consistent with the
`chooseBioCmirror` function in the `utils` package.

## Installation

Currently, the package can only be found on GitHub. To install it, use the
following:

```{r, eval=FALSE}
if (!requireNamespace("BiocManager", quietly=TRUE))
    install.packages("BiocManager")

BiocManager::install("Bioconductor/BioCmirrors")
```


## Quick Start

```{r,include=TRUE,results="hide",message=FALSE,warning=FALSE}
library(BioCmirrors)
```

## Mirror Health Checks

The `checkBioCmirror` function checks the health status of a Bioconductor
mirror including the main Bioconductor URL:

```{r}
url <- "https://bioconductor.org"
checkBioCmirror(mirror = url)
```

The function can also be run interactively, where it will display a list
of mirrors to choose from:


```{r, eval=FALSE}
checkBioCmirror()
#' Secure BioC mirrors 
#' 
#'  1: 0-Bioconductor (World-wide) [https]   2: USA (Boston) [https]               
#'  3: Germany (Gottingen) [https]           4: Japan (Wako) [https]               
#'  5: Taiwan (Hsinchu) [https]              6: China (Peking) [https]             
#'  7: China (Nanjing) [https]               8: China (Hefei Anhui) [https]        
#'  9: Norway (Bergen) [https]              10: Denmark (Aalborg) [https]          
#' 11: Sweden (Umea) [https]                12: (other mirrors)                    
#' 
#' 
#' Selection: 3
#' https://ftp.gwdg.de/pub/misc/bioconductor/packages/bioc/src/contrib/PACKAGES 
#'                                                                         TRUE 
```

## List of Mirrors

The `listBioCmirrors` function returns a list of all available Bioconductor
mirrors:

```{r}
mirrors <- listBioCmirrors()
mirrors
```

The `tibble` output can be used to filter the mirrors by country:

```{r}
mirrors |>
    dplyr::filter(.data[["Country"]] == "USA")
```

## Mirror Statistics

The `BioCmirrorStats` function returns details about the `PACKAGES` file
time stamp, the number of packages available, and the number of packages
mirrored. The function can be used to check the status of a specific mirror. In
this example, we reproduce the output of `utils::chooseBioCmirror()` by
creating a named string with the URL of the mirror in Germany:

```{r}
url <- "https://ftp.gwdg.de/pub/misc/bioconductor"
de_mirror <- c("Germany (Gottingen) [https]" = url)
stats <- BioCmirrorStats(mirror = de_mirror)
stats
```

As shown, the packages on the mirror are up-to-date, and there are no
missing packages. 

# Session Info

<details> <summary> Click to expand </summary>

```{r}
sessionInfo()
```

</details>
